### 2013-03-25 doc/dissertation/document/chapters/mc_background/mc_background.tex
adding evolution of a solution for the direct method in background

@@

>>>>

\subsection{Direct Method: Evolution of a Solution}
\label{subsec:direct_evolution}

As a means of visually demonstrating the direct Monte Carlo method,
consider a 2-dimensional thermal diffusion problem with sources on the
left and right hand sides of the domain and a smaller uniform source
as shown in Figure~\ref{fig:heat_setup}.
\begin{figure}[h!]
  \begin{center}
    \scalebox{1.0}{ \input{heat_eq_setup.pdftex_t} }
  \end{center}
  \caption{\textbf{Problem setup for 2D heat equation.}
    \textit{Dirichlet conditions are set for the temperature on all 4
      boundaries of the Cartesian grid. Background source of 1.0
      present. $50 \times 50$ grid.}}
  \label{fig:heat_setup}
\end{figure}
For this problem, the number of histories used to compute the solution
at each state in the domain was increased from 1 to 1000 in order to
show its effects on the solution and the statistical nature of the
method. Figure~\ref{fig:direct_evolution} gives these results.
\begin{figure}[h!]
  \begin{center}
    \includegraphics[width=4in]{direct_evolution.png}
  \end{center}
  \caption{\textbf{Direct Monte Carlo solution to the heat equation
      with varying numbers of histories.} \textit{Top left: 1 history
      per state. Top right: 10 histories per state. Bottom left: 100
      histories per state. Bottom right: 1000 histories per state.}}
  \label{fig:direct_evolution}
\end{figure}
As the number of histories used per state is increased, the
statistical variance of the solutions is decreased as more tallies are
made. At 1000 histories per state, enough tallies have been made to
generate a reasonable estimate for the structure of the solution.

@@

\subsection{Adjoint Method: Evolution of a Solution}
\label{subsec:adjoint_evolution}
